Resources for Data-Driven \\Search-Based Software Engineering

### 2018-01-20 doc/tex/msr18/main.tex

\maketitle
\pagestyle{plain}
% \input{samplebody-conf}
\section{Introduction}
This paper initiates a new shared resource for the Mining Software
Repositories (MSR) community.
Fig1 shows the Github repoistory \href{https://github.com/ai-se/ResourceDataDrivenSBSE}{ai-se/ResourcesDataDrivenSBSE}. In this report we describe the why and
what of this resource. Our intent is that, as a result
of this paper, we receive many pull requests that extend
this repository into a useful resource for   MSR.

@@

\begin{figure*}[!t]
{\center
\includegraphics[width=5.5in]{img/page1.png}}
\caption{http://tiny.cc/sbse = our Github-based repository for resources relating to data-drive Search-based SE 
currently contains 89 artifacts divided into 13 groups. References in the right-hand column come from this paper.
For each of the above, there exists papers showing published baselines. Each of these baselines can be viewed as challenge problems:
how many of these baselines can you repeat/ improve/ refute? To contribute, researchers need only modify the repository then submit a pull request. }
\end{figure*}
XXX optimisation

>>>>

\maketitle
\pagestyle{plain}
% \input{samplebody-conf}

\begin{figure*}[!t]
{\center
\includegraphics[width=5.5in]{img/page1.png}}
\caption{Our Github-based repository (http://tiny.cc/sbse) for resources relating to data-drive Search-based SE 
currently contains 89 artifacts divided into 13 groups. References in the right-hand column come from this paper.
For each of the above, there exists papers showing published baselines. Each of these baselines can be viewed as challenge problems:
how many of these baselines can you repeat/ improve/ refute?  }\label{fig:one}
\end{figure*}

\section{Introduction}
This paper introduces tiny.cc/sbse, a  new shared resource for the Mining Software
Repositories (MSR) community shown in Figure~\ref{fig:one}.

The resource has   taken several years to build. Prior to its
existence, we tested   our data-driven search-based SE
prototypes on tiny toy tasks such as the ZDT~\cite{xx} and DTLZ suites~\cite{xx}. These toy tasks have some useful
properties-- for example, the DTLZ tasks can expand to any number of decisions and objectives.
However, 
those models proved not to be of interest to reviewers from SE venues.

Recently we have much more success in terms of novel research results
(and publications at SE forums) after 
expanding that collection
to include models
of (e.g.) software product lines, requirements, and
agile software projects. 
As such we have found it to be a very useful resource
which we now offer to the MSR community.

This paper describes that resource,    how to use it,
and why the general MSR community might find it insightful.
The resource is a Github repository and our intent is that it
attracts enough attention that  other researchers  clone, modify, the submit  pull requests back to that site. In this way, we hope it grows
into a useful resource for MSR.

\section{Why is this Interesting?}

@@

XXX optimisation
